---
title: "Assignment3"
author: "Mayerli Mercado"
date: "`r format(Sys.time(), '%y-%b-%d, %I:%M %p')`"
---

## __R Tutorial 3__
```{r, message=FALSE}
library(ggplot2)
data("trees")
head(trees)
```

__Q1.__ Create a histogram showing the distribution of Girth.
```{r, message=FALSE}
color = c("orange")
ggplot(trees, aes(Girth)) + 
  geom_histogram(fill = color) +
  labs(title = "Distribution of Girth") + 
  theme_bw() +
  theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12)
)
```

__Q2.__ Create a histogram showing the distribution of Volume.
```{r, message=FALSE}
color = c("lightblue")
ggplot(trees, aes(Volume)) + 
  geom_histogram(fill = color) +
  labs(title = "Distribution of Volume") + 
  theme_bw() +
  theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12)
)
```
__Q3.__ Create a scatterplot showing the relationship between Girth and Volume.
```{r, message=FALSE}
ggplot(trees, aes(Girth, Volume)) + 
  geom_point() +
  labs(title = "Relationship between Girth and Volume") + 
  theme_bw() +
  theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12)
)
```

__Q4.__ Use the Shapiro–Wilk test to assess whether Volume is normally distributed. Report the p-value and state whether the data are normally distributed.
```{r, warning=FALSE}
tv <- aov(Volume ~ Volume, data = trees)
summary(tv)
```
```{r}
resid_anova <- residuals(tv)
shapiro.test(resid_anova)
```
The p-value (p=0.003579) is less than 0.05, the null hypothesis is rejected and it is determined that the data is not normally distributed.<br>

__Q5.__ Repeat the Shapiro–Wilk test for Girth. Report the p-value and state whether Girth is normally distributed.
```{r, warning=FALSE}
tg <- aov(Girth ~ Girth, data = trees)
summary(tg)
```
```{r}
resid_anova <- residuals(tg)
shapiro.test(resid_anova)
```
The p-value (p=0.08893) is greater than 0.05, the null hypothesis is not rejected and it is determined that the data is normally distributed.<br>