---
title: "Assignment2"
author: "Mayerli Mercado"
date: "`r format(Sys.time(), '%y-%b-%d, %I:%M %p')`"
---

## __R Tutorial 2__
```{r, message=FALSE}
library(dplyr)
library(gapminder)
```

__Q1.__ What class is the gapminder dataset?
```{r}
class(gapminder)
```

__Q2.__ Filter a section of gapminder with a life expectancy smaller than 29.
```{r}
gapminder |> 
  filter(lifeExp < 29)
```

__Q3.__ Filter the data for the country __Rwanda__ and for years greater than 1979.
```{r}
gapminder |> 
  filter(country == "Rwanda",
         year > 1979)
```


__Q4.__ Create a new dataset from __gapminder__ excluding the column __gdpPercap.__
```{r}
excluding <- gapminder |> 
  select(!(gdpPercap))
excluding
```

__Q5.__ Arrange the dataset in ascending order of lifeExp.
```{r}
ascending <- gapminder |> 
  arrange(lifeExp)
ascending
```

__Q6.__ Arrange the dataset in descending order of lifeExp.
```{r}
descending <- gapminder |> 
  arrange(desc(lifeExp))
descending
```

__Q7.__ Create a new dataset with only the columns year and lifeExp.
```{r}
newgapminder <- gapminder |> 
  select(year,
         lifeExp)
newgapminder
```

__Q8.__ Filter the dataset for the country Cambodia and show only the columns year and lifeExp.
```{r}
Cambodia <- gapminder |> 
  filter(country == "Cambodia") |> 
  select(year, lifeExp)
Cambodia
```

__Q9.__ Select only the countries in Africa.
```{r}
Africa <- gapminder |> 
  filter(continent == "Africa") |> 
  select(country)
Africa
```

__Q10.__ Create a new column called lifeExp_months that shows life expectancy in months.
```{r}
lifeExp_months <- gapminder |> 
  mutate(lifeExp_months = lifeExp * 12)
lifeExp_months |> 
  select(lifeExp_months, lifeExp, everything())
```